---
title: "Visualize Data"
author: "Tyler Busby"
format: gfm
---


```{r}
#| label: setup
#| include: false
library(tidyverse)
```



## Your Turn 0

Add a setup chunk that loads the tidyverse packages.


```{r}
head(mpg)
```


## Your Turn 1

Run the code on the slide to make a graph. Pay strict attention to spelling, capitalization, and parentheses!

```{r}
ggplot(mpg) +
  geom_point(aes(x = displ, 
                 y = hwy))
```


## Your Turn 2

Replace this scatterplot with one that draws boxplots. Use the cheatsheet. Try your best guess.

```{r}
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = class, y = hwy))
```


## Your Turn 3

Make a histogram of the `hwy` variable from `mpg`. Hint: do not supply a y variable.

```{r}
ggplot(data = mpg) +
  geom_histogram(mapping = aes(x = hwy))
```

## Your Turn 4

Use the help page for `geom_histogram` to make the bins 2 units wide.

```{r}
ggplot(data = mpg) +
  geom_histogram(mapping = aes(x = hwy),
                 binwidth = 2,
                 fill = "blue",
                 alpha = 0.2,
                 color = "black")
```


## Your Turn 5

Add `color`, `size`, `alpha`, and `shape` aesthetics to your graph. Experiment.  

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, 
                           y = hwy,
                           shape = class,
                           color = class,
                           size = year,
                           alpha = trans),
             labs(x = "Engine Size Displacment",
                  y = "Highway Mileage",
                  color = "Class of Vehicle") +
               theme_classic())
```

## Help Me

What do `facet_grid()` and `facet_wrap()` do? 
(run the code, interpret, convince your group)

```{r}
# Makes a plot that the commands below will modify
q <- ggplot(mpg) + geom_point(aes(x = displ, y = hwy))

q + facet_grid(. ~ cyl) # makes one row and four columns by cyl
q + facet_grid(drv ~ .) # makes three rows by drv and one column
q + facet_grid(drv ~ cyl) # makes three rows by drv and four columns by cyl
q + facet_wrap(~ class) # makes a plot for each class
```


## Your Turn 6

Make a bar chart `class` colored by `class`. Use the help page for `geom_bar` to choose a "color" aesthetic for class.

```{r}
ggplot(data = mpg) +
  geom_bar(aes(x = class, fill = class)) +
  guides(fill = "none") +
  labs(x = "Class of Vehicle",
       y = "Number of Vehicles in Sample") +
  theme_bw()
```

## Quiz

What will this code do?

```{r}
ggplot(mpg) + 
  geom_point(aes(displ, hwy)) + # creates a scatterplot of displ and hwy
  geom_smooth(aes(displ, hwy)) #adds a lineplot to the data by displ and hwy
  ggsave("example.jpg") #saves the created plot as "example.jpg"
```


***

# Take aways

You can use this code template to make thousands of graphs with **ggplot2**.

```{r eval = FALSE}
ggplot(data = <DATA>) +
  <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))
```